### 2021-03-18 ch/2-related-work.tex
Address most of Novi's feedback

\section{Modification of labels for Fairness enforcement}\label{modification-of-labels-for-fairness-enforcement}
Independently of \citet{pedreshi2008discrimination}, but with a similar intention,
\citet{kamiran2009classifying} considered discrimination in classification.
Their goal is to modify the dataset so that any classifier trained on it will be ``fair'',
which is measured with a fairness metric on the test set predictions.
The test set is drawn from the same distribution as the training set.
To demonstrate their method, they use the ``German credit dataset''
where the task is to classify people as a good or a bad credit risk.

The authors formulate the problem as it was later done in other works on fairness as well:
there is a set of features, a binary class label
and a special \emph{sensitive attribute} which determines the demographic group.
The sensitive attribute \(s\) is assumed to be binary in the derivation,
but does not have to be.
\(s=0\) refers to the group vulnerable to discrimination and \(s=1\) to all other individuals.
It is further assumed that one of the class labels is generally desirable;
for example, it might correspond to being accepted for a credit or being given bail.
This class label is being referred to as the positive label: \(y = 1\).

@@

\citet{kamishima2012fairness} take a closer look
at the ways in which training data can be biased (or more generally of poor quality) and condense it to three main causes:
\emph{prejudice}, \emph{underestimation} and \emph{negative legacy}.
(Let \(x\) be the non-sensitive features.)

@@

More specifically, the stated goal of \citet{zemel2013learning} is
to achieve both \emph{group fairness} (in the sense of Demographic Parity)
and \emph{individual fairness} (in the sense of treating similar people similarly),
as \citet{dwork2012fairness} did before.
Let \(z\) denote the learned fair representation.
The condition for fairness is then
\begin{align}
  \label{eq:fair-representation}
  P(s=0|z=z') = P(s=1|z=z') ~.
\end{align}
\citet{zemel2013learning} propose to map the biased inputs \(x\) to \emph{prototypes} in the same space as \(x\).
The probability for being assigned to a particular prototype
must be the same for inputs with \(s=0\) and for \(s=1\).
Based on a given distance function (or similarity measure),
inputs are more likely to be assigned to prototypes that are close-by.
The classification task is then based entirely on the prototypes (the fair representation \(z\)).
In their work, a linear model is used to map the prototypes to the outcomes \(y\).
Aside from the distance function, the whole model has therefore only two kinds of parameters:
the locations of the prototypes and the weights in the linear model.
These parameters are all optimised together.
The objective function consists of three terms:
the first enforcing Demographic Parity via the prototype locations,
the second ensuring that the prototypes are close to the inputs
and the third targeting a good accuracy by adapting the weights of the classifier.
%
The experiments are done on the German credit dataset, the Adult / Census Income dataset
and a dataset based on the Heritage Health Prize milestone 1 challenge
where the goal is to predict how many days a given person will spend in the hospital in a year.
% The proposed methods performs better in these experiments
% than the methods from \citet{kamiran2009classifying} and the method from \citet{kamishima2012fairness}.
% However, they do not compare against \citet{calders2010three},
% presumably because those methods rely on the sensitive attribute for making predictions,
% which can be considered an unfair advantage.

@@

\section{Refinement of previous ideas}%
\label{sec:refinement-on-previous-ideas-for-fair-classification-and-fair-representations}
\subsection{Fair classifiers continued}
Following the initial publications,
several works refined the ideas that had been presented there.
In a very influential work by \citet{zafar2017fairnessconstraints}
present a more efficient way to train a fair classifier.
At the beginning, the authors explicitly discuss the tension
between the two goals of making fair predictions and not making use of the sensitive attributes.
Using sensitive attributes to make predictions
is referred to as \emph{Disparate Treatment} by the authors.
Algorithms like the one by \citet{calders2009building} use the sensitive
attribute during prediction to achieve a very high degree of fairness, but this can have a
lot of problems from a legal perspective and can also easily go wrong.
Thus, \citet{zafar2017fairnessconstraints} set themselves the goal of achieving fairness while making use of the sensitive attributes
as little as possible, i.e.~avoiding Disparate Treatment.

In order to train a fair classifier, \citet{zafar2017fairnessconstraints} use a proxy of the definition of
\ac{DP} that is easier to optimise during training, namely the covariance
between the sensitive attribute and the predicted score \(f\):
\begin{align}
  \label{eq:zafar-constraint}
  Cov(s, f) = \mathbb{E}[(s - \bar{s})f] - \mathbb{E}[(s - \bar{s})]\bar{f} \approx 
  \frac{1}{N} \sum\limits_{i=1}^{N} (s_i - \bar{s}) \cdot f_i
\end{align}
We will call this the covariance criterion.
The classifier can then be trained in two ways.
The first way is to minimise the loss that enforces accuracy
with the constraint that the covariance criterion is below a certain threshold.
The other way is to minimise the covariance criterion
with the constraint that the accuracy is above a certain threshold.
The paper includes experiments with these techniques with SVM and Logistic Regression classifiers
on the Adult/Census Income dataset and the Bank marketing dataset.
In the Bank marketing dataset, the task is to predict whether a client will respond to marketing for a term deposit,
based on 20 attributes of the person.
The sensitive attribute is \emph{age}.
The proposed algorithm performs similarly to the best previous algorithms (similar in fairness and accuracy),
notably without making use of the sensitive attribute for predictions.
% This is an impressive achievement.

In a follow up work, \citet{zafar2017fairnesstreatment} adapt their work to enforce \acf{EOdds},
as defined in \citet{hardt2016equality}.
(However, it is here referred to as ``Disparate Mistreatment'' instead of ``equalised odds''.)
As in the previous work, they define a tractable proxy for this measure.
To this end, they first define a function \(g\) that measures
how well the class label \(y \in \{0, 1\}\) and the predicted score for a data point \(0 \leq f(x) \leq 1\) agree:
\begin{align}
  \label{eq:zafar-constraint-2}
  g(y, x) = \min \left(0, \left(y - \tfrac{1}{2}\right) \cdot \left(f(x) - \tfrac{1}{2}\right)\right)
\end{align}
Subtracting \(\tfrac{1}{2}\) is necessary to centre the values around \(0\).
The proxy for \ac{EOdds} is then the covariance between the sensitive attribute and \(g\).
\(g\) can also be modified to only take into account cases with \(y=1\) which corresponds to Equality of Opportunity.
The paper contains experiments on the ProPublica/COMPAS dataset~\citep{angwin2016machine}.
The task for this dataset is to predict
whether a criminal offender committed another misconduct or felony within two years,
based on personal information that includes age, gender, race and past criminal history.
% The authors compare the proposed method to an implementation of the algorithm from \citet{hardt2016equality}.
% In the Equality of Opportunity task, the approach by \citet{hardt2016equality} performs better
% (lower discrimination, similar accuracy).
% The better performance is likely at least partially explained
% by \citet{hardt2016equality} using the sensitive attribute for predictions.
% The evaluation metric is
% the difference in FPR (false positive rate) and the difference in FNR (false negative rate) between the two groups.
% Hardt et al.~achieve an FPR difference of 0.02 at 66\% accuracy while Zafar et al.~achieve an FPR difference of
% 0.06 at the same 66\% accuracy.
% For Equalised Odds,
% the proposed approach achieves higher accuracy but also higher discrimination than in \citet{hardt2016equality}.
% One limiting factor that the authors identify is the size of the dataset:
% the degree of discrimination cannot be accurately estimated by the algorithm if the dataset is small.

@@

The paper provides an algorithm that constructs a fair classifier (for the provided fairness definition)
given a structural equation model (a form of causal model).
The resulting classifier is fair \emph{by construction}.
However, note that this procedure does not lead to true individual fairness,
because the influence of \(p\) is only removed at the population level
(except in the case where all descendants of \(p\) are completely removed).
Individual decisions can still be unfair as long as it balances out overall.

The authors provide a number of properties of their method with corresponding proofs.
For example, if the influence of \(p\) on \(x\) is additive and linear,
any predictor of the form \[g(x - \mathbb{E}[x|do(p=p')])\] has no proxy discrimination.
Though no experiments are included in the paper.

@@

A contemporary paper by \citet{kusner2017counterfactual} approaches the problem differently.
In this paper, a new fairness criterion which they call ``counterfactual fairness''
is defined making use of causal reasoning.
For the definition, they assume access to a causal model
that can be used to compute \emph{counterfactuals} (for example a structural equation model).
This is in contrast to \citet{kilbertus2017avoiding} who relied on just \emph{interventions}.
The causal model depends on unobserved background variables \(U\),
non-sensitive features \(x\) and a sensitive attribute \(s\).
A predictor \(\hat{y}\) is then \emph{counterfactually fair}
if the following equality of counterfactual probabilities holds:
\begin{align}
  \label{eq:counterfactual-fairness}
  P(\hat{y}_{s=i}(U) = 1|x, s=i)=P(\hat{y}_{s=j}(U) = 1|x, s=i)
\end{align}
where \(i, j \in \{0, 1\}\) and \(i \neq j\).

@@

The authors provide an algorithm to construct a classifier that satisfies counterfactual fairness.
However, constructing the causal model remains the major weakness of this approach,
and is currently only really feasible for tabular data.
% The authors point to existing literature on the topic and give some additional vague guidelines.
As experiments, the algorithm is applied to the Law School Success dataset.
The task is to predict the first year average grade (FYA) in law school
given the GPA before law school and the score on the entrance exam (LSAT).
Also known are race and sex, which are not supposed to be used to make predictions.
% Logistic regression is used for the classifier.

% The authors construct two causal models.
% In both models, race and sex influence all three test scores GPA, LSAT and FYA.
% In the first model, there is only one background variable that the authors call \emph{knowledge}.
% This variable influences the three test scores but does not influence the race or sex.
% The second model is a fully deterministic model
% where we have three background variables which play the role of additive error terms.
% The three error terms may be correlated.
If the underlying causal model is taken as true,
the trained fair classifiers are automatically completely counterfactually fair.
% The second model achieves a slightly lower prediction error than the first model
% (RMSE of 0.918 vs 0.929).
Additionally, two (unfair) baseline models were trained:
one trained on only \(x\) and the other trained on \(x\) and \(s\);
those baseline models indeed turn out to be not counterfactually fair.

The work by \citet{chiappa2019path} can be seen as a refinement of \citet{kilbertus2017avoiding}.
Instead of disallowing influence of \emph{nodes}, this works disallows certain \emph{paths} to influence the outcome.
The path pointing directly from the sensitive attribute to the outcome is not allowed,
but paths via certain variables are allowed.
An example for such a permissible variable comes from the Berkeley admissions dataset:
overall, the data shows that women were admitted at lower rates,
but this turned out to be mediated by department choice.
Women were applying to more competitive departments and thus had lower acceptance rates.
The choice of department \(C\) is here an admissible variable:
the outcome \(Y\) may depend on it.
So, a path from \(S\) (gender) to \(Y\) via \(C\) is permissible, and our fairness definition should reflect this.
Counterfactual fairness \citep{kusner2017counterfactual} would in this case arguably give the wrong answer.
In certain simple cases, path-specific fairness is equivalent to the criterion from \citet{kilbertus2017avoiding}.
The problem remains that the causal model needs to be constructed
and permissible variables need to be identified manually.

@@

\citet{kim2019learning} also consider the problem of learning from biased data (and evaluating on unbiased data).
While they do not formulate the problem as a fairness problem,
it is equivalent to enforcing fairness in the presence of severe sampling bias.
Their main motivating example is the Coloured MNIST dataset:
in this dataset, digits are randomly coloured in the test set,
but in the training set there is a one-to-one correspondence between digit class and colour.
A na\"ive classifier will learn to predict colour instead of digit class.
The proposed method is very similar to \citet{ganin2016domain} and \citet{edwards2016censoring},
if we think of the colours as forming different domains
(\ie, the \emph{red} domain contains all red digits, etc.).
The goal is then to learn a domain-independent representation.
The main difference to previous work is an additional entropy loss term in the adversarial loss.

@@

>>>>

\section{Modification of labels for Fairness enforcement}\label{modification-of-labels-for-fairness-enforcement}
Independently of \citet{pedreshi2008discrimination}, but with a similar intention,
\citet{kamiran2009classifying} considered discrimination in classification.
Their goal is to modify the dataset so that any classifier trained on it will be ``fair'',
which is measured with a fairness metric on the test set predictions.
The test set is drawn from the same distribution as the training set.
To demonstrate their method, they use the ``German credit dataset''~\citep{Dua:2017}
where the task is to classify people as a good or a bad credit risk.

The authors formulate the problem as it was later done in other works on fairness as well:
there is a set of features \(x\), a binary class label \(y\)
and a special \emph{sensitive attribute} \(s\) which determines the demographic group.
The sensitive attribute \(s\) is assumed to be binary in the derivation,
but does not have to be.
\(s=0\) refers to the group vulnerable to discrimination and \(s=1\) to all other individuals.
It is further assumed that one of the class labels is generally desirable;
for example, it might correspond to being accepted for a credit or being given bail.
This class label is being referred to as the positive label: \(y = 1\).

@@

\citet{kamishima2012fairness} take a closer look
at the ways in which training data can be biased (or more generally of poor quality) and condense it to three main causes:
\emph{prejudice}, \emph{underestimation} and \emph{negative legacy}.

@@

More specifically, the stated goal of \citet{zemel2013learning} is
to achieve both \emph{group fairness} (in the sense of Demographic Parity)
and \emph{individual fairness} (in the sense of treating similar people similarly),
as \citet{dwork2012fairness} did before.
Let \(z\) denote the learned fair representation.
The condition for fairness is then
\begin{align}
  \label{eq:fair-representation}
  P(s=0|z=z') = P(s=1|z=z') ~.
\end{align}
\citet{zemel2013learning} propose to map the biased inputs \(x\) to \emph{prototypes} in the same space as \(x\).
The probability for being assigned to a particular prototype
must be the same for inputs with \(s=0\) and for \(s=1\).
Based on a given distance function (or similarity measure),
inputs are more likely to be assigned to prototypes that are close-by.
The classification task is then based entirely on the prototypes (the fair representation \(z\)).
In their work, a linear model is used to map the prototypes to the outcomes \(y\).
Aside from the distance function, the whole model has therefore only two kinds of parameters:
the locations of the prototypes and the weights in the linear model.
These parameters are all optimised together.
The objective function consists of three terms:
the first enforcing Demographic Parity via the prototype locations,
the second ensuring that the prototypes are close to the inputs
and the third targeting a good accuracy by adapting the weights of the classifier.
%
The experiments are done on the German credit dataset, the Adult / Census Income dataset
and a dataset based on the Heritage Health Prize milestone 1 challenge~\citep{heritagehealth}
where the goal is to predict how many days a given person will spend in the hospital in a year.
% The proposed methods performs better in these experiments
% than the methods from \citet{kamiran2009classifying} and the method from \citet{kamishima2012fairness}.
% However, they do not compare against \citet{calders2010three},
% presumably because those methods rely on the sensitive attribute for making predictions,
% which can be considered an unfair advantage.

@@

\section{Refinement of previous ideas}%
\label{sec:refinement-on-previous-ideas-for-fair-classification-and-fair-representations}
\subsection{Fair classifiers continued}
Following the initial publications,
several works refined the ideas that had been presented there.
In a very influential work by \citet{zafar2017fairnessconstraints}
present a more efficient way to train a fair classifier.
The authors explicitly discuss the tension
between the two goals of making fair predictions and not making use of the sensitive attributes.
Using sensitive attributes to make predictions
is referred to as \emph{Disparate Treatment} by the authors.
Algorithms like the one by \citet{calders2009building} use the sensitive
attribute during prediction to achieve a very high degree of fairness, but this can have a
lot of problems from a legal perspective and can also easily go wrong.
(Making use of \(s\) comes close to \emph{direct discrimination} discussed above.)
Thus, \citet{zafar2017fairnessconstraints} set themselves the goal of achieving fairness while making use of the sensitive attributes
as little as possible, i.e.~avoiding Disparate Treatment.

In order to train a fair classifier, \citet{zafar2017fairnessconstraints} use a proxy of the definition of
\ac{DP} that is easier to optimise during training, namely the covariance
between the sensitive attribute and the predicted score \(f\):
\begin{align}
  \label{eq:zafar-constraint}
  Cov(s, f) = \mathbb{E}[(s - \bar{s})f] - \mathbb{E}[(s - \bar{s})]\bar{f} \approx 
  \frac{1}{N} \sum\limits_{i=1}^{N} (s_i - \bar{s}) \cdot f_i
\end{align}
The authors refer to this as the covariance criterion.
The classifier can then be trained in two ways.
The first way is to minimise the loss that enforces accuracy
with the constraint that the covariance criterion is below a certain threshold.
The other way is to minimise the covariance criterion
with the constraint that the accuracy is above a certain threshold.
The paper includes experiments with these techniques with SVM and Logistic Regression classifiers
on the Adult/Census Income dataset and the Bank marketing dataset~\citep{Dua:2017}.
In the Bank marketing dataset, the task is to predict whether a client will respond to marketing for a term deposit,
based on 20 attributes of the person.
The sensitive attribute is \emph{age}.
The proposed algorithm performs similarly to the best previous algorithms (similar in fairness and accuracy),
notably without making use of the sensitive attribute for predictions.
% This is an impressive achievement.

In a follow up work, \citet{zafar2017fairnesstreatment} adapt their work to avoid ``disparate mistreatment''.
Avoiding disparate mistreatment is equivalent to enforcing \acf{EOdds}
as defined in the contemporary work by \citet{hardt2016equality}.
As in the previous work, they define a tractable proxy for this measure.
To this end, they first define a function \(g\) that measures
how well the class label \(y \in \{0, 1\}\) and the predicted score for a data point \(0 \leq f(x) \leq 1\) agree:
\begin{align}
  \label{eq:zafar-constraint-2}
  g(y, x) = \min \left(0, \left(y - \tfrac{1}{2}\right) \cdot \left(f(x) - \tfrac{1}{2}\right)\right)
\end{align}
Subtracting \(\tfrac{1}{2}\) is necessary to centre the values around \(0\).
The proxy for \ac{EOdds} is then the covariance between the sensitive attribute and \(g\).
\(g\) can also be modified to only take into account cases with \(y=1\) which corresponds to Equality of Opportunity.
The paper contains experiments on the ProPublica/COMPAS dataset~\citep{angwin2016machine}.
The task for this dataset is to predict
whether a criminal offender committed another misconduct or felony within two years,
based on personal information that includes age, gender, race and past criminal history.
% The authors compare the proposed method to an implementation of the algorithm from \citet{hardt2016equality}.
% In the Equality of Opportunity task, the approach by \citet{hardt2016equality} performs better
% (lower discrimination, similar accuracy).
% The better performance is likely at least partially explained
% by \citet{hardt2016equality} using the sensitive attribute for predictions.
% The evaluation metric is
% the difference in FPR (false positive rate) and the difference in FNR (false negative rate) between the two groups.
% Hardt et al.~achieve an FPR difference of 0.02 at 66\% accuracy while Zafar et al.~achieve an FPR difference of
% 0.06 at the same 66\% accuracy.
% For Equalised Odds,
% the proposed approach achieves higher accuracy but also higher discrimination than in \citet{hardt2016equality}.
% One limiting factor that the authors identify is the size of the dataset:
% the degree of discrimination cannot be accurately estimated by the algorithm if the dataset is small.

@@

The paper provides an algorithm that constructs a fair classifier (for the provided fairness definition)
given a structural causal model \citep{pearl2009causality}.
The resulting classifier is fair \emph{by construction}.
However, note that this procedure does not lead to true individual fairness,
because the influence of \(p\) is only removed at the population level
(except in the case where all descendants of \(p\) are completely removed).
Individual decisions can still be unfair as long as it balances out overall.

The authors show a number of properties of their method with corresponding proofs.
(Though no experiments are included in the paper.)
For example, if the influence of \(p\) on \(x\) is additive and linear,
any predictor of the form \[g(x - \mathbb{E}[x|do(p=p')])\] has no proxy discrimination.

@@

A contemporary paper by \citet{kusner2017counterfactual} approaches the problem differently.
In this paper, a new fairness criterion which they call ``counterfactual fairness''
is defined making use of causal reasoning.
For the definition, they assume access to a causal model
that can be used to compute \emph{counterfactuals} (for example a structural equation model \citep{kaplan2008structural}).
This is in contrast to \citet{kilbertus2017avoiding} who relied on just \emph{interventions}.
(According to Pearl's causal hierarchy \citep{pearl2019seven},
counterfactuals require a deeper level of causal information than interventions.)
The causal model depends on unobserved background variables \(U\),
non-sensitive features \(x\) and a sensitive attribute \(s\).
A predictor \(\hat{y}\) is then \emph{counterfactually fair}
if the following equality of counterfactual probabilities holds:
\begin{align}
  \label{eq:counterfactual-fairness}
  P(\hat{y}_{s=i}(U) = 1|x, s=i)=P(\hat{y}_{s=j}(U) = 1|x, s=i)
\end{align}
where \(i, j \in \{0, 1\}\) and \(i \neq j\).

@@

The authors provide an algorithm to construct a classifier that satisfies counterfactual fairness.
However, constructing the causal model remains the major weakness of this approach,
and is currently only really feasible for tabular data.
% The authors point to existing literature on the topic and give some additional vague guidelines.
As experiments, the algorithm is applied to the Law School Success dataset~\citep{wightman1998lsac}.
The task is to predict the first year average grade (FYA) in law school
given the GPA before law school and the score on the entrance exam (LSAT).
Also known are race and sex, which are not supposed to be used to make predictions.
% Logistic regression is used for the classifier.

% The authors construct two causal models.
% In both models, race and sex influence all three test scores GPA, LSAT and FYA.
% In the first model, there is only one background variable that the authors call \emph{knowledge}.
% This variable influences the three test scores but does not influence the race or sex.
% The second model is a fully deterministic model
% where we have three background variables which play the role of additive error terms.
% The three error terms may be correlated.
If the given causal model is taken as the true model,
then it follows that the trained fair classifiers are fair by construction.
% The second model achieves a slightly lower prediction error than the first model
% (RMSE of 0.918 vs 0.929).
Additionally, two (unfair) baseline models were trained:
one trained on only \(x\) and the other trained on \(x\) and \(s\);
those baseline models indeed turn out to be not counterfactually fair.

The work by \citet{chiappa2019path} can be seen as a refinement of \citet{kilbertus2017avoiding}.
Instead of disallowing influence of \emph{nodes}, this works disallows certain \emph{paths} to influence the outcome.
The path pointing directly from the sensitive attribute to the outcome is not allowed,
but paths via certain variables are allowed.
An example for such a permissible variable comes from the Berkeley admissions dataset~\citep{bickel1975sex}:
overall, the data shows that women were admitted at lower rates,
but this turned out to be mediated by department choice.
Women were applying to more competitive departments and thus had lower acceptance rates.
The choice of department \(C\) is here an admissible variable:
the outcome \(Y\) may depend on it.
So, a path from \(S\) (gender) to \(Y\) via \(C\) is permissible, and our fairness definition should reflect this.
Counterfactual fairness \citep{kusner2017counterfactual} would in this case arguably give the wrong answer.
In certain simple cases, path-specific fairness is equivalent to the criterion from \citet{kilbertus2017avoiding}.
The problem remains that the causal model needs to be constructed
and permissible variables need to be identified manually.

@@

\citet{kim2019learning} also consider the problem of learning from biased data (and evaluating on unbiased data).
While they do not formulate the problem as a fairness problem,
it is equivalent to enforcing fairness in the presence of severe sampling bias.
Their main motivating example is the Coloured MNIST dataset;
a dataset derived from the MNIST dataset~\citep{lecun1994mnist}.
In this dataset, digits are randomly coloured in the test set,
but in the training set there is a one-to-one correspondence between digit class and colour.
A na\"ive classifier will learn to predict colour instead of digit class.
The proposed method is very similar to \citet{ganin2016domain} and \citet{edwards2016censoring},
if we think of the colours as forming different domains
(\ie, the \emph{red} domain contains all red digits, etc.).
The goal is then to learn a domain-independent representation.
The main difference to previous work is an additional entropy loss term in the adversarial loss.

@@

As the authors point out,
the goal of machine learning should be to identify natural, deep, robust structures in reality,
instead of relying on superficial correlations.
(This dichotomy is sometimes framed as \emph{correlation} vs \emph{causality},
where ``causality'' takes on a very broad meaning that encompasses any kind of fundamental structure in reality.)
Methods for invariance learning can be framed as trying to learn a more fundamental structure
than the dataset at first seems to show.
By aiming to be invariant to specific environments/subgroups/domains (denoted by the variable \(s\)),
they can be seen as making the claim that \(s\) does not represent a natural structure,
but is merely an artifact of the data generation process.
Furthermore, the ground-centric view of dataset bias can be understood as
aiming to identify the fundamental structures and aiming to be invariant to everything else.

### 2021-03-18 ch/4-structure.tex
Address most of Novi's feedback

\section{Overcoming severe sampling bias with a representative set}\label{sec:nifr}
In the setting from the previous paper \citep{kehrenberg2020tuning},
labels were untrustworthy because they had been flipped;
a phenomenon we referred to as \emph{label bias}.
However, flipped labels is not the only way that labels can become untrustworthy.
Another way is \emph{sampling bias}, which is the subject of \citet{kehrenberg2020nullsampling} and \citet{kehrenberg2020zeroshot} (\twochaprefs{ch:paper2}{ch:paper3}).

@@

The distribution matching is realized with adversarial networks which compare batches of samples,
in order to try to distinguish data drawn from the training set and the deployment set.
This process requires balanced batches as an inductive bias,
becaus the network will only learn the intended difference between training and deployment set,
if the drawn batches exhibit this difference.
For example, if batches drawn from Coloured MNIST differ not in colour but in digit class,
then distribution matching will learn to change digit shapes.
Balancing batches from the training set is easily possible with the available labels,
but those are not available for the deployment set,
so we use clustering techniques to identify the different groups in the deployment set,
and then draw samples for the batches at equal rate from all clusters.
It is important to note here that imperfections in the clustering are not a problem
as long as the show on average the intended difference between training and deployment set.

>>>>

\section{Overcoming severe sampling bias with a representative set}\label{sec:nifr}
In the setting from the previous paper \citep{kehrenberg2020tuning},
labels were untrustworthy because they had been flipped;
a phenomenon we referred to as \emph{label bias}.
However, flipping labels is not the only way that labels can become untrustworthy.
Another way is \emph{sampling bias}, which is the subject of \citet{kehrenberg2020nullsampling} and \citet{kehrenberg2020zeroshot} (\twochaprefs{ch:paper2}{ch:paper3}).

@@

The distribution matching is realized with adversarial networks which compare batches of samples,
in order to try to distinguish data drawn from the training set and the deployment set.
This process requires balanced batches as an inductive bias,
because the network will only learn the intended difference between training and deployment set,
if the drawn batches exhibit this difference.
For example, if batches drawn from Coloured MNIST differ not in colour but in digit class,
then distribution matching will learn to change digit shapes.
Balancing batches from the training set is easily possible with the available labels,
but those are not available for the deployment set,
so we use clustering techniques to identify the different groups in the deployment set,
and then draw samples for the batches at equal rate from all clusters.
It is important to note here that imperfections in the clustering are not a problem
as long as the show on average the intended difference between training and deployment set.
